---
title: "Homework1"
author: "Yiran Jin"
date: "2026-09-24"
output: github_document
---

# Problem 1
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

## Description of the Penguins Dataset
The `penguins` dataset contains data on penguins from the Palmer Archipelago.
There are important variables include `species`, which identifies the penguin species
(Adelie, Chinstrap, and Gentoo), `island`, which identifies the island
(Biscoe, Dream, and Torgersen), `bill_length_mm` and `bill_depth_mm`, which
measure bill dimensions, `flipper_length_mm`, which measures flipper length
in millimeters, and `body_mass_g`, which measures body mass in grams.

The dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns.
The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`
mm.

## Scatter Plot for Penguins
```{r, warning=FALSE}
ggplot(
  penguins,
  aes(
    x = bill_length_mm,
    y = flipper_length_mm,
    color = species
  )
) +
  geom_point() +
  labs(
    x = "Bill length (mm)",
    y = "Flipper length (mm)",
    color = "Species",
    title = "Flipper Length vs. Bill Length"
  )
ggsave(
  "penguins_scatterplot.png",
  width = 7,
  height = 5
)
```
# Problem 2
```{r, warning=FALSE}
library(tidyverse)

set.seed(123)

# Create the data frame
mydataframe_df <- tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  character_var = c(
    "a", "b", "c", "d", "e",
    "f", "g", "h", "i", "j"
  ),
  factor_var = factor(
    c("low", "medium", "high", "low", "medium", "high", "low", "medium", "high", "low"
    )
  )
)
```

## Take the mean of each variable
```{r, warning=FALSE}
mean(pull(mydataframe_df, norm_samp))
mean(pull(mydataframe_df, norm_samp_pos))
mean(pull(mydataframe_df, character_var))
mean(pull(mydataframe_df, factor_var))
```

```{r, warning=FALSE, results='hide'}
as.numeric(pull(mydataframe_df, norm_samp_pos))
as.numeric(pull(mydataframe_df, character_var))
as.numeric(pull(mydataframe_df, factor_var))
```

The mean works for the numeric and logical variables, but it does not work for the character and factor variables. R treats TRUE as 1 and FALSE as 0, so the mean of the logical variable can be calculated. Converting the logical variable to numeric gives 1s and 0s. The character variable cannot be converted to numeric because it contains text and the factor variable is converted to its internal level codes rather than meaningful numerical values.
